\documentclass[10pt]{article}

%% PACKAGES %%


\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

% Font
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
 
% Page Layout
\usepackage{geometry}
\geometry{
	a4paper,
	top=10mm,
	bottom=10mm
}

\usepackage{hyperref}
\urlstyle{same}

\usepackage{etaremune}
\pagestyle{empty}

\usepackage[document]{ragged2e}

\begin{document}

\moveleft.5\hoffset\centerline{\huge\bf Dinesh Vijayakumar} % Your name at thetop
\moveleft.5\hoffset\centerline{{\bf Ph}:+91-8220858395, {\bf Email}:vpdinesh1990@live.in}
\moveleft.5\hoffset\centerline{\href{https://www.dineshvijayakumar.xyz/}{https://www.dineshvijayakumar.xyz/}}
\hrule

\begin{minipage}[t]{0.40\textwidth}
\vspace{5pt}

\section*{Courses \& Certifications}
\begin{itemize}
\item Coursera: {\bf Kotlin for Java Developers} - Aug 2021, {\bf Behavioral Finance} - Dec 2017
\item Java: Sun Certified Java Profession-5.0, June 2009, Credential ID - SR5715191
\end{itemize}

\section*{Technical Skills}
\begin{itemize}
\item {\bf Languages}: Java, Kotlin
\item {\bf Build tools}: Apache Ant, Gradle
\item {\bf Cloud Computing}: AWS
\item {\bf Developer Tools}: Git, IntelliJ, VS Code, Docker
\item {\bf Big Data Technologies}: Apache Spark, EMR, S3, Apache Parquet
\item {\bf Frameworks}: DI(Guice, Dagger), Junit, TestNG 
\end{itemize}
\section*{Education}
{\sl B.E. Computer Science Engineering 2011,} \href{https://gct.ac.in/}{Government College of Technology(GCT) Coimbatore, India} 
\begin{itemize}
\item Operating Systems, Data Structure and Algorithms, Web Services, Computer Networks, Artificial Intelligence
\end{itemize}
 

\section*{Academic Achievements}
\begin{itemize}
\item Graduated with Distinction in B.E with a CGPA of 8.98/10.
\item Received {\bf Best Student} award from Tata Consultancy Services for excellent academic record at GCT, Coimbatore.
\end{itemize}

\section*{Awards}
\begin{itemize}
\item Last Mile Defect Destroyer - 2017 for improving code quality and developing a command-line (CLI) tool for troubleshooting application failures.
\item Srujan Contest 2011 - 2nd Prize for implementing the idea titled {\sl Product Recommendations through Social Network} with a prototype. 
\end{itemize}

\end{minipage}
\hfill
\begin{minipage}[t]{0.58\textwidth}
\vspace{5pt}
\section*{Experience}
\begin{flushright}
\RaggedRight {\bf Senior Software Development Engineer, DC Tech,  2021 - Present, Bangalore, India} 


\RaggedRight Developing a Warehouse Management System to support bulk fulfillment of Grocery and Amazon Warehousing \& Distribution(AWD) supply chain networks through Distribution Centers. Specfically focusing on the following domains besides leading the org-wide Operational/Engineering Excellence Initiative.
\begin{itemize}
\item {Produce Grading}
\item ICQA
\item {Problem Solve}
\end{itemize}
\RaggedRight {\bf Sr. SDE, Amazon AI - CodeGuru, 2019 - 2021, Seattle, WA, US }

\RaggedRight Worked on the Code Guru Reviewer Service to enable following capabilities.

\begin{itemize}
\item Bitbucket Support - April 2020
\item \href{https://aws.amazon.com/blogs/aws/find-your-most-expensive-lines-of-code-amazon-codeguru-is-now-generally-available/}{GA Launch - May 2020}
\item \href{https://aws.amazon.com/blogs/aws/amazon_codeguru_reviewer_updates_new_java_detectors_and_cicd_integration_with_github_actions/}{CI/CD Vendor Integration (GitHub Actions) - April 2021}
\end{itemize}
\RaggedRight {\bf Sr. SDE, Amazon - Last Mile Technology, 2015-2019, Seattle, WA, US }
\begin{itemize}
\item Enabled Automated Surge Pricing to hire Delivery Partners(DP) for delivering Prime Now and Amazon.com orders with cost savings of {\bf ~11 cents} (surge cost per hour) on average.
\item Led the initiative {\bf Last Mile Data Lake} to build a cost-effective solution with estimated savings of ~700k \$ by having teams move away from using AWS Redshift.
\item Automated the invoicing and disbursement of payments for Delivery Service Providers(DSP), processing MM of dollars every month.
\end{itemize}

\RaggedRight {\bf SDE, AWS - Elastic Block Store(EBS), 2014-2015, Seattle, WA, US}
\begin{itemize}
\item Enabled Idempotency Support for EBS Volume API and developed Server Isolation Workflow to remove faulty EBS nodes from serving customer traffic
\item Added features to Gossip Protocol-based distributed failure detection and node discovery system to achieve high availability({\bf 99.9\%}).
\end{itemize}
\RaggedRight {\bf SDE, Amazon - WW Transportation, 2011-2014, Hyderabad, India }
\begin{itemize}
\item Delivered capability to handle mis-routed/damaged packages from 3P carriers for adjusting delivery schedule of Amazon.com customer orders and issuing refunds/replacements. 
\end{itemize}
\end{flushright}


\end{minipage}
\end{document}
\documentclass[]{article}

